---
title: "EAL Performance Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    source_code: embed
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(shiny)
library(shinyBS)
library(bubbles)
library(colorspace)
library(janitor)
```

Sidebar {.sidebar}
=======================================================================

### cran.rstudio.com

The streaming data is a 1-week-delayed livestream of download
logs from  cran.rstudio.com. The server code for that service is at [jcheng5/cransim](https://github.com/jcheng5/cransim).


```{r}
# Rate at which to flag high download traffic
airbnb_data = read_csv("nyc_airbnb.csv")

airbnb_data = airbnb_data %>%
  mutate(rating = review_scores_location / 2) %>%
  select(boro = neighbourhood_group, neighbourhood, rating, price, room_type,
         lat, long) %>%
  filter(!is.na(rating)) 

boros = airbnb_data %>% 
  group_by(boro) %>% 
  tally() %>% 
  adorn_totals("row", name = "Cumulative") %>% 
  select(boro)

textInput("boro_choosing", label = h3("Pick App"), 
          placeholder = "Input Key Business Function", value = "Manhattan")

selectInput("boro_choice", label = h3("Select boro"),
            choices = boros, selected = "Cumulative")


# for analysis
place_holder = "Insert App Description Here"
textAreaInput("text_to_explain", 
              label = h4("App Description Here"), 
              placeholder = place_holder)

bsTooltip(id = "text_to_explain", title = "For Use on Second Tab", 
          placement = "bottom", trigger = "hover")

addTooltip(session, id = "text_to_explain", title = "For Use on Second Tab",
           placement = "bottom", trigger = "hover")


tags$style(HTML('#predict{background-color:#0c64a3}'))
actionButton("predict","Evaluate")

```


Dashboard
=======================================================================

Row
-----------------------------------------------------------------------

### Apps Coded in Domino {.value-box}

```{r}
# downloadRate is a reactive expression that computes the download
# rate during this dashboard's lifetime.

# Emit the download rate

#apps coded in domino/days since deploy/cumulative spend

getvalue = reactive ({
  airbnb_data 
})

renderValueBox({
  good = getvalue() %>% 
    group_by(boro) %>% 
    summarize(price = mean(price)*100) %>% 
    adorn_totals("row", name = "Cumulative") %>% 
    filter(boro == input$boro_choice)
  valueBox(
    value = as.integer(good[2]),
    icon = "fa-area-chart",
    color = if (as.integer(good[2]) >= 0) "warning" else "primary"
  )
})
```

### Transformation Investment {.value-box}

```{r}
# dlCount is a reactive expression that keeps track of the total
# number of rows that have ever appeared through pkgStream.

getvalue = reactive ({
  airbnb_data 
})

renderValueBox({
  good = getvalue() %>% 
    group_by(boro) %>% 
    summarize(price = mean(price)*100) %>% 
    adorn_totals("row", name = "Cumulative") %>% 
    filter(boro == input$boro_choice)
  valueBox(
    value = as.integer(good[2]),
    icon = "fa-area-chart",
    color = if (as.integer(good[2]) >= 0) "warning" else "primary"
  )
})
```

### Total Investment {.value-box}

```{r}
# usrCount is a reactive expression that keeps an approximate
# count of all of the unique users that have been seen since the
# app started.


getvalue = reactive ({
  airbnb_data 
})

renderValueBox({
  good = getvalue() %>% 
    group_by(boro) %>% 
    summarize(price = mean(price)) %>% 
    adorn_totals("row", name = "Cumulative") %>% 
    filter(boro == input$boro_choice)
  valueBox(
    value = as.integer(good[2]),
    icon = "fa-area-chart",
    color = if (as.integer(good[2]) >= 0) "warning" else "primary"
  )
})


```

Row
-----------------------------------------------------------------------

### Downloads per sec (last 5 min)

```{r}
getguage = reactive ({
  airbnb_data 
})

renderGauge({
  rate <- getguage() %>% 
    group_by(boro) %>% 
    summarize(price = mean(price)) %>% 
    adorn_totals("row", name = "Cumulative") %>% 
    filter(boro == input$boro_choice)
  gauge(as.integer(rate[2]),
        min = 0, 
          max = 200, 
          sectors = gaugeSectors(success = c(0.5, 1), 
                                 warning = c(0.3, 0.5),
                                 danger = c(0, 0.3)
  ))
})


```

### Average downloads per user

```{r}
app_name <- reactive({
  app_namer <- regex(pattern = input$boro_choosing)
  app_namer
})

renderGauge({
  rate <- getguage() %>% 
    group_by(boro) %>% 
    summarize(price = mean(price)) %>% 
    adorn_totals("row", name = "Cumulative") %>% 
    filter(boro == app_name())
  gauge(as.integer(rate[2]),
        min = 0, 
        max = 200, 
        sectors = gaugeSectors(success = c(0.5, 1), 
                                 warning = c(0.3, 0.5),
                                 danger = c(0, 0.3)
  ))
})
```

### Downloads per sec (last 5 min)

```{r}


renderGauge({
  rate <- getguage() %>% 
    group_by(boro) %>% 
    summarize(price = mean(price)) %>% 
    adorn_totals("row", name = "Cumulative") %>% 
    filter(boro == input$boro_choice)
  gauge(as.integer(rate[2]),
        min = 0,
        max = 200, 
        symbol = '%',
        label = "Hello",
        sectors = gaugeSectors(success = c(0.5, 1), 
                                 warning = c(0.3, 0.5),
                                 danger = c(0, 0.3)
  ))
})
```

Row
-----------------------------------------------------------------------

### Popularity by package (last 5 min) {data-width=700}

```{r}
renderBubbles({
    
  df <- getguage() %>%
    group_by(boro, neighbourhood) %>%
    tally(sort = T) %>% 
    mutate(new =
    case_when(input$boro_choice == "Cumulative" ~ "Cumulative",
              TRUE ~ boro)) %>% 
    filter(new == input$boro_choice) %>% 
    head(40)

  bubbles(df$n, 
          df$neighbourhood, 
          key = df$neighbourhood,
          color = rainbow_hcl(nrow(df)))
})
```

### Percent of downloads (last 5 min) {data-width=340}

```{r}
library(packcircles)
library(viridis)
renderPlot ({

data = getguage() %>%  
   group_by(boro, neighbourhood) %>%
    tally(sort = T) %>% 
    mutate(new =
    case_when(input$boro_choice == "Cumulative" ~ "Cumulative",
              TRUE ~ boro)) %>% 
    filter(new == input$boro_choice) 

packing <- circleProgressiveLayout(data$n, sizetype='area')
data <- cbind(data, packing)
dat.gg <- circleLayoutVertices(packing, npoints=50)


ggplot() + 
  geom_polygon(data = dat.gg, 
               aes(x, y, group = id, fill=as.factor(id)), colour = "black", alpha = 0.6) +
  scale_fill_manual(values = magma(nrow(data))) +
  geom_text(data = data, aes(x, y, size=n, label = neighbourhood)) +
  scale_size_continuous(range = c(1,4)) +
  theme_void() + 
  theme(legend.position="none") +
  coord_equal()    
})
```

Proposal Assessment 
=======================================================================

Row
-----------------------------------------------------------------------

### Prediction 

### Business Impact Score (Partial Depedency Plot)


Row
-----------------------------------------------------------------------

### Supplementary Data
```{r}
```





Metric Definitions 
=======================================================================

Row
-----------------------------------------------------------------------

### __Fragility__

### Modernization

### Brand Equity

Row
-----------------------------------------------------------------------
### __Additional Considerations__

Here I'll have to put some sort of information